---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ongoal

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ongoal)](https://CRAN.R-project.org/package=ongoal)
[![Codecov test coverage](https://codecov.io/gh/topepo/ongoal/branch/main/graph/badge.svg)](https://app.codecov.io/gh/topepo/ongoal?branch=main)
[![R-CMD-check](https://github.com/topepo/ongoal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/topepo/ongoal/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

```{r load, include = FALSE}
library(ongoal)
```

ongoal makes `r nrow(on_goal)` data points available for Pittsburgh Penguins games where the it was determined whether a shot was on goal (i.e., made it to the goaltender) or not (i.e., missed or blocked). Data are from seasons 2015-2016, 2016-2017, and 2017-2018. 

Several other columns were recorded related to the game, player, and shot. The data are not perfect; the determination of power play duration were manually calculated and may not be completely accurate.  

## Installation

You can install the development version of ongoal:

``` r
require(pak)
pak::pak("topepo/ongoal")
```

## Example

Here's a look at the data: 

```{r example}
library(ongoal)
str(on_goal)
```

There's also a visualization function (based on [Bill Tran's function](https://raw.githubusercontent.com/mrbilltran/the-win-column/master/nhl_rink_plot.R)):

```{r rink}
suppressPackageStartupMessages(library(dplyr))
set.seed(1)
on_goal %>% 
  filter(abs(angle) < 20 & distance < 40) %>% 
  sample_n(500) %>% 
  plot_nhl_shots(emphasis = on_goal, alpha = 1 / 2)

```

## Future plans

I might make a different version of the data and plotting function that use the absolute x coordinate so that we only have to plot half the rink. 



## Code of Conduct
  
Please note that the ongoal project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
  
